---
title: "1st-year-survey"
author: "Preetha"
date: "12/7/2020"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE, 
                      message = FALSE)
```

```{r load-packages}
library(tidyverse)
```

```{r load-data}
first <- readr::read_csv('data/survey.csv')
```

```{r, include = FALSE}
newfirst <- first %>% 
  mutate(college = `Are you enrolled in Trinity College of Arts and Sciences or the Pratt School of Engineering?`,
         hispanic = `Are you of Hispanic/Latino/Spanish origin?`,
         race = `How would you best describe yourself?`,
         gender = `What is your gender?`,
         sexor = `What is your sexual orientation?`,
         firstgen = `Are you a first-generation college student?`,
         athlete = `Are you a recruited varsity athlete?`,
         int = `Are you an international student?`,
         state = `Which state do you live in (please enter the postal abbreviation)?`,
         zip = `What is the ZIP Code of your home address?`,
         city = `What is your home city?`,
         country = `What is your home country?`,
         community = `What type of community are you from?`,
         income = `What do you estimate is your immediate family's total annual income?`,
         finaid = `Do you receive financial aid from Duke?`,
         major = `Which major are you most inclined towards?`,
         whyduke = `Which of the following most influenced your decision to attend Duke?`,
         greek = `How interested are you in Greek life at Duke?`,
         slgs = `How interested are you in non-Greek selective living groups at Duke?`,
         rush = `Are you more or less likely to rush if the recruitment process were to be online?`,
         whyrush = `What is your primary motivation for wanting to rush?`,
         livingwhere = `Which of the following best describes your living situation this semester?`,
         whyhome = `What was your primary reason for staying home?`,
         springliving = `Are you planning to come to campus/Durham in the spring?`,
         springplans = `What are your plans for the spring?`,
         covidrelief = `Did you receive additional COVID-19 relief funds from Duke? (in addition to financial aid package)`,
         amount = `What do you think of the amount received?`,
         testpos = `Have you tested positive for COVID-19 (while on campus)?`,
         knowpos = `Has someone you know tested positive for COVID-19 (while on campus)?`,
         compactOp = `Share your opinions on... - The Duke Compact`,
         enforcementOp = `Share your opinions on... - Duke's enforcement of the Duke Compact`,
         housingOp = `Share your opinions on... - First-year fall housing arrangements`,
         inperson = `How many in-person classes are you in this semester?`,
         focus = `Are you in a FOCUS?`,
         inpersonfocus = `How many of your FOCUS classes are in-person (not including the FOCUS “dinner”)?`,
         findcommunity = `Have you been able to find community this year?`,
         communitywhere = `Where have you primarily found community?`,
         pandemiccommunity = `How much do you think the pandemic has negatively affected your ability to find community?`,
         wearmask = `How likely are you to abide by the following elements of the Duke Compact: - Wearing a mask or face covering in all public spaces`,
         usesymmon = `How likely are you to abide by the following elements of the Duke Compact: - Monitoring and reporting symptoms through the SymMon app`,
         avoidgather = `How likely are you to abide by the following elements of the Duke Compact: - Avoiding large gatherings of 10+ people`,
         covidrelief = `Did you receive additional COVID-19 relief funds from Duke? (in addition to financial aid package)`,
         dodistance = `How likely are you to abide by the following elements of the Duke Compact: - Engaging in physical distancing`,
         peersmask = `How likely are your peers to abide by the following elements of the Duke Compact: - Wearing a mask or face covering in all public spaces`,
         peerssymmon = `How likely are your peers to abide by the following elements of the Duke Compact: - Monitoring and reporting symptoms through the SymMon app`,
         peersavoidgather = `How likely are your peers to abide by the following elements of the Duke Compact: - Avoiding large gatherings of 10+ people`,
         peersdistance = `How likely are your peers to abide by the following elements of the Duke Compact: - Engaging in physical distancing`,
         report = `How likely are you to report violations to the Duke Compact?`,
         summerplans = `Were your summer and/or travel plans affected by the pandemic?`,
         jobloss = `Has any member of your household lost their job or been furloughed due to the pandemic?`,
         coviddeath = `Have any of your family members or close contacts died from COVID-19?`,
         gpa = `What was your high school GPA (scaled on a 0 to 4.00 scale)?`,
         actorsat = `Did you take the SAT or ACT?`,
         sat = `What was your SAT combined score?`,
         act = `What was your ACT composite score?`,
         schooltype = `What type of secondary school did you attend?`,
         summerplans = `Were your summer and/or travel plans affected by the pandemic?`,
         collegecoun = `Did you hire a private college admissions counselor during the admissions process?`,
         numberapps = `How many colleges and universities did you apply to?`,
         acceptances = `How many colleges and universities were you accepted to?`,
         ed = `Did you apply to Duke via the Early Decision process?`,
         waitlist = `Were you accepted off the waitlist from Duke?`,
         firstchoice = `Was Duke your first choice?`,
         legacy = `Did any of your parents or siblings attend Duke?`,
         religion = `Which best describes your religion?`,
         howreligious = `How religious would you say you are?`,
         political = `How would you describe your political beliefs?`,
         voted = `Did you / are you planning to vote in the 2020 election?`,
         president = `Who did you vote for / who are you planning to vote for?`,
         wherevote = `Did you / are you planning to vote at your home or in Durham?`,
         primaryvote = `Did you vote in the primary election?`,
         lifestyle = `Have you done any of the following?`,
         mentalhealth = `Have you received treatment for your mental health before?`,
         continuedtreatment = `Are you currently receiving treatment for your mental health?`,
         chronicle = `In which format do you read The Chronicle?`)
```

```{r, include = FALSE}
newfirst
```
### Analysis

```{r fig.height=6, fig.width=7, include = FALSE}
newfirst %>% 
  ggplot(newfirst, mapping = aes(x = primaryvote, fill = (factor(political ,levels=c("Very conservative", "Somewhat conservative", "Moderate","Somewhat liberal", "Very liberal")))))+
  geom_bar(position= "fill") +
  labs(title = "did you vote in the primaries? vs political leaning", 
       x = "", y = "") +
  scale_fill_discrete(name = "political leaning") +
  scale_x_discrete(na.translate = FALSE) +
  coord_flip() +
  theme_minimal()
```

## Who are Duke's Trump and Biden voters? 

```{r religion-and-pres, fig.height=6, fig.width=7, echo = FALSE}
newfirst %>% 
  ggplot(data=subset(newfirst, !is.na(president)), mapping = aes(x = (factor(president,levels=c("Joe Biden","Donald Trump"))), fill = religion))+
  geom_bar(position= "fill") +
  labs(title = "more support for trump among religiously affiliated students", 
       subtitle = "NOTE: Howie Hawkins and Jo Jorgenson removed from data set.
            One student voted for each candidate.",
       x = "", y = "") +
  scale_fill_discrete(name = "student's religious affiliation") +
  scale_x_discrete(na.translate = FALSE) +
  coord_flip() +
  theme_minimal()
```

```{r religiousity-and-pres, fig.height=6, fig.width=7, echo = FALSE}
newfirst %>% 
  ggplot(data=subset(newfirst, !is.na(president)), mapping = aes(x = (factor(president ,levels=c("Joe Biden","Donald Trump"))), fill = (factor(howreligious ,levels=c("Not at all religious", "Not very religious", "Somewhat religious", "Religious", "Very religious")))))+
  geom_bar(position= "fill") +
  labs(title = "more support for trump among religious students", 
       subtitle = "NOTE: Howie Hawkins and Jo Jorgenson removed from data set.
            One student voted for each candidate.",
       x = "", y = "") +
  scale_fill_discrete(name = "religiousity") +
  scale_x_discrete(na.translate = FALSE) +
  coord_flip() +
  theme_minimal()
```

The students who voted for Trump overwhelmingly identified themselves with a 
religion (versus agnostic or atheist). A similar breakdown in visible when 
looking at support for Trump with an eye to religiosity; well over 50% of Biden 
voters identify themselves as "Not at all religious" or "Not very religious" 
while for Trump, that number is below 40%.

```{r fig.height=6, fig.width=7}
newfirst %>% 
  ggplot(data=subset(newfirst, !is.na(president)), mapping = aes(x = (factor(income ,levels=c("Above $500,000","$250,000-$500,000", "$125,000-$250,000", "$80,000-$125,000","$40,000-$80,000", "Below $40,000"))), fill = (factor(president ,levels=c("Donald Trump","Howie Hawkins","Joe Biden","Jo Jorgenson")))))+
  geom_bar(position= "fill") +
  labs(title = "income and presidential vote",
       x = "", y = "") +
  scale_fill_discrete(name = "presidential vote") +
  scale_x_discrete(na.translate = FALSE) +
  coord_flip() +
  theme_minimal()
```
Biden voters are present in every income bracket and Trump voters are present
in almost every income bracket, with a slightly greater representation in the 
"Above $500,000" category. 

```{r fig.height=6, fig.width=7}
newfirst %>% 
  ggplot(newfirst, mapping = aes(x = (factor(president ,levels=c("Joe Biden","Donald Trump"))), fill = legacy))+
  geom_bar(position= "fill") +
  labs(title = "political leaning and legacy status", 
       x = "", y = "") +
  coord_flip() +
  scale_x_discrete(na.translate = FALSE) +
  theme_minimal()
```

Slightly more legacy students voted for Trump, though this may be more 
attributable to their income bracket (legacy students are overrepresented in
higher income brackets) than their status as legacy students.

```{r fig.height=6, fig.width=7}
newfirst %>% 
  ggplot(newfirst, mapping = aes(x = (factor(president ,levels=c("Joe Biden","Donald Trump"))), fill = sexor))+
  geom_bar(position= "fill") +
  labs(title = "political leaning and sexual orientation", 
       x = "", y = "") +
  coord_flip() +
  scale_x_discrete(na.translate = FALSE) +
  theme_minimal()
```

In our sample, about 25% of students that voted for Biden identify with a 
sexual orientation other than "Heterosexual". 

```{r fig.height=6, fig.width=7}
newfirst %>% 
  ggplot(data=subset(newfirst, !is.na(president)), mapping = aes(x = community, fill = (factor(president,levels=c("Donald Trump", "Howie Hawkins", "Joe Biden","Jo Jorgenson")))))+
  geom_bar(position= "fill") +
  labs(title = "community and presidential vote", 
       x = "", y = "") +
  scale_fill_discrete(name = "presidential vote") +
  coord_flip() +
  scale_x_discrete(na.translate = FALSE) +
  theme_minimal()
```

All students who voted for a candidate other than Biden came from a suburban 
community.

```{r fig.height=6, fig.width=7}
newfirst %>% 
  ggplot(data=subset(newfirst, !is.na(president)), mapping = aes(x = (factor(greek ,levels=c("Extremely interested", "Very interested", "Moderately interested", "Slightly interested", "Not interested at all"))), fill = (factor(president,levels=c("Donald Trump", "Howie Hawkins", "Joe Biden","Jo Jorgenson")))))+
  geom_bar(position= "fill") +
  labs(title = "interest in greek life & presidential vote", 
       x = "", y = "") +
  scale_fill_discrete(name = "presidential vote") +
  coord_flip() +
  scale_x_discrete(na.translate = FALSE) +
  theme_minimal()
```

Biden voters show varying degrees of interest in greek life while Trump voters 
are more likely to indicate that they are "Very interested" in greek life.

```{r fig.height=6, fig.width=7}
newfirst %>% 
  ggplot(data=subset(newfirst, !is.na(president)), mapping = aes(x = (factor(coviddeath,levels=c("Yes", "No"))), fill = (factor(president,levels=c("Donald Trump", "Jo Jorgenson", "Joe Biden","Howie Hawkins")))))+
  geom_bar(position= "fill") +
  labs(title = "family/friend death from covid and presidential vote", 
       x = "", y = "") +
  scale_fill_discrete(name = "presidential vote") +
  coord_flip() +
  scale_x_discrete(na.translate = FALSE) +
  theme_minimal()
```

Every respondent who indicated they had lost someone to COVID voted for Biden.

```{r fig.height=6, fig.width=7, include = FALSE}
newfirst %>% 
  ggplot(data=subset(newfirst, !is.na(president)), mapping = aes(x = jobloss, fill = (factor(president,levels=c("Howie Hawkins", "Jo Jorgenson", "Joe Biden","Donald Trump")))))+
  geom_bar(position= "fill") +
  labs(title = "job loss from covid and presidential vote", 
       x = "", y = "") +
  scale_fill_discrete(name = "presidential vote") +
  coord_flip() +
  scale_x_discrete(na.translate = FALSE) +
  theme_minimal()
```

```{r fig.height=6, fig.width=7, include=FALSE}
newfirst %>% 
  ggplot(newfirst, mapping = aes(x = (factor(president,levels=c("Howie Hawkins", "Jo Jorgenson", "Joe Biden","Donald Trump"))), fill = finaid))+
  geom_bar(position= "fill") +
  labs(title = "presidential vote and financial aid status", 
       x = "", y = "") +
  coord_flip() +
  scale_x_discrete(na.translate = FALSE) +
  theme_minimal()
```


## Legacy students are more likely to indicate that they are very conservative

```{r fig.height=6, fig.width=7}
newfirst %>% 
  ggplot(newfirst, mapping = aes(x = (factor(political ,levels=c("Very liberal", "Somewhat liberal", "Moderate","Somewhat conservative", "Very conservative"))), fill = legacy))+
  geom_bar(position= "fill") +
  labs(title = "political leaning and legacy status", 
       x = "", y = "") +
  coord_flip() +
  scale_x_discrete(na.translate = FALSE) +
  theme_minimal()
```

Of the students who indicated that they are "Very conservative," over 60% have a
parent or sibling that attended Duke. 

```{r fig.height=6, fig.width=7, include=FALSE}
newfirst %>% 
  ggplot(newfirst, mapping = aes(x = (factor(greek ,levels=c("Extremely interested", "Very interested", "Moderately interested", "Slightly interested", "Not interested at all"))), fill = (factor(income ,levels=c("Above $500,000","$250,000-$500,000", "$125,000-$250,000", "$80,000-$125,000","$40,000-$80,000", "Below $40,000")))))+
  geom_bar(position= "fill") +
  labs(title = "income and interest in greek life", 
       x = "", y = "") +
  scale_fill_discrete(name = "income level") +
  coord_flip() +
  theme_minimal()
```

```{r fig.height=6, fig.width=7, include=FALSE}
newfirst %>% 
  ggplot(newfirst, mapping = aes(x = legacy, fill = (factor(income ,levels=c("Above $500,000","$250,000-$500,000", "$125,000-$250,000", "$80,000-$125,000","$40,000-$80,000", "Below $40,000")))))+
  geom_bar(position= "fill") +
  labs(title = "legacy status and income", 
       x = "", y = "") +
  scale_fill_discrete(name = "income level") +
  coord_flip() +
  theme_minimal()
```

## Who are Duke's conservatives and liberals? (I hate this title too dw)

```{r polleaning and religion, fig.height=6, fig.width=7, echo = FALSE}
newfirst %>% 
  ggplot(newfirst, mapping = aes(x = (factor(political ,levels=c("Very liberal", "Somewhat liberal", "Moderate","Somewhat conservative", "Very conservative"))), fill = (factor(howreligious ,levels=c("Not at all religious", "Not very religious", "Somewhat religious", "Religious", "Very religious")))))+
  geom_bar(position= "fill") +
  labs(title = "increased liberal views, decreased religiosity", 
       x = "", y = "") +
  scale_fill_discrete(name = "religiousity") +
  scale_x_discrete(na.translate = FALSE) +
  coord_flip() +
  theme_minimal()
```

Reflecting national trends, the results from our survey show that students who
identify themselves as more liberal (on a scale of Very conservative to 
Very liberal), also identify themselves as less religious. 

```{r fig.height=6, fig.width=7}
newfirst %>% 
  ggplot(newfirst, mapping = aes(x = (factor(political ,levels=c("Very liberal", "Somewhat liberal", "Moderate","Somewhat conservative", "Very conservative"))), fill = sexor))+
  geom_bar(position= "fill") +
  labs(title = "political leaning and sexual orientation", 
       x = "", y = "") +
  coord_flip() +
  scale_x_discrete(na.translate = FALSE) +
  theme_minimal()
```

Students who identify as politically moderate to very liberal are more likely to 
identify with a sexual orientation other than "heterosexual."

```{r fig.height=6, fig.width=7}
newfirst %>% 
  ggplot(newfirst, mapping = aes(x = (factor(political ,levels=c("Very liberal", "Somewhat liberal", "Moderate","Somewhat conservative", "Very conservative"))), fill = finaid))+
  geom_bar(position= "fill") +
  labs(title = "political leaning and financial aid status", 
       x = "", y = "") +
  coord_flip() +
  scale_x_discrete(na.translate = FALSE) +
  theme_minimal()
```

Students who identify as politically moderate to very liberal are more likely to 
be receiving some form of financial aid.

```{r fig.height=6, fig.width=7, include=FALSE}
newfirst %>% 
  ggplot(newfirst, mapping = aes(x = major, fill = (factor(political ,levels=c("Very liberal", "Somewhat liberal", "Moderate","Somewhat conservative", "Very conservative")))))+
  geom_bar(position= "fill") +
  labs(title = "intended major and political leaning", 
       x = "", y = "") +
  scale_fill_discrete(name = "political leaning") +
  coord_flip() +
  theme_minimal()
```

```{r fig.height=6, fig.width=7, include=FALSE}
newfirst %>% 
  ggplot(newfirst, mapping = aes(x = (factor(greek ,levels=c("Extremely interested", "Very interested", "Moderately interested", "Slightly interested", "Not interested at all"))), fill = (factor(political ,levels=c("Very conservative", "Somewhat conservative", "Moderate","Somewhat liberal", "Very liberal")))))+
  geom_bar(position= "fill") +
  labs(title = "interest in greek life & political leaning", 
       x = "", y = "") +
  scale_fill_discrete(name = "political leaning") +
  coord_flip() +
  theme_minimal()
```

```{r fig.height=6, fig.width=7, include=FALSE}
newfirst %>% 
  ggplot(newfirst, mapping = aes(x = (factor(slgs ,levels=c("Extremely interested", "Very interested", "Moderately interested", "Slightly interested", "Not interested at all"))), fill = (factor(political ,levels=c("Very conservative", "Somewhat conservative", "Moderate","Somewhat liberal", "Very liberal")))))+
  geom_bar(position= "fill") +
  labs(title = "interest in slgs & political leaning", 
       x = "", y = "") +
  scale_fill_discrete(name = "political leaning") +
  coord_flip() +
  theme_minimal()
```

```{r fig.height=6, fig.width=7, include=FALSE}
newfirst %>% 
  ggplot(newfirst, mapping = aes(x = (factor(greek ,levels=c("Extremely interested", "Very interested", "Moderately interested", "Slightly interested", "Not interested at all"))), fill = sexor))+
  geom_bar(position= "fill") +
  labs(title = "interest in greek life & sexual orientation", 
       x = "", y = "") +
  scale_fill_discrete(name = "political leaning") +
  coord_flip() +
  theme_minimal()
```

```{r fig.height=6, fig.width=7}
newfirst %>% 
  ggplot(newfirst, mapping = aes(x = community, fill = (factor(political ,levels=c("Very conservative", "Somewhat conservative", "Moderate","Somewhat liberal", "Very liberal")))))+
  geom_bar(position= "fill") +
  labs(title = "community and political leaning", 
       x = "", y = "") +
  scale_fill_discrete(name = "political leaning") +
  coord_flip() +
  theme_minimal()
```

All students in our survey who identify as "Very conservative" or "Somewhat 
conservative" come from a suburban community.

```{r fig.height=6, fig.width=7, include=FALSE}
newfirst %>% 
  ggplot(newfirst, mapping = aes(x = collegecoun, fill = (factor(income ,levels=c("Above $500,000","$250,000-$500,000", "$125,000-$250,000", "$80,000-$125,000","$40,000-$80,000", "Below $40,000")))))+
  geom_bar(position= "fill") +
  labs(title = "hired college counselor and income", 
       x = "", y = "") +
  scale_fill_discrete(name = "income level") +
  coord_flip() +
  theme_minimal()
```

```{r fig.height=6, fig.width=7}
newfirst %>% 
  ggplot(newfirst, mapping = aes(x = college, fill = (factor(political, levels=c("Very conservative", "Somewhat conservative", "Moderate","Somewhat liberal", "Very liberal")))))+
  geom_bar(position= "fill") +
  labs(title = "Trinity is slightly more liberal", 
       x = "", y = "") +
  scale_fill_discrete(name = "political leaning") +
  coord_flip() +
  theme_minimal()
```

Students who identify as "Somewhat liberal" or "Very liberal" are representative
of over 75% of Trinity students, while the same group is approx. 60% of 
Pratt's student body.

```{r fig.height=6, fig.width=7, include=FALSE}
newfirst %>% 
  ggplot(newfirst, mapping = aes(x = (factor(political, levels=c("Very liberal", "Somewhat liberal", "Moderate","Somewhat conservative", "Very conservative"))), fill = whyduke))+
  geom_bar(position= "fill") +
  labs(title = "why duke and political leaning", 
       x = "", y = "") +
  coord_flip() +
  theme_minimal()
```

## How do liberals/conservatives feel about the Duke Compact? (I hate this too)

```{r home-and-pres-vote, fig.height=6, fig.width=7, echo = FALSE, include = FALSE}
newfirst %>% 
  ggplot(newfirst, mapping = aes(x = wherevote, fill = president))+
  geom_bar(position= "fill") +
  labs(title = "more biden voters among students who elected to vote in Durham", 
       x = "", y = "") +
  coord_flip() +
  theme_minimal()
```

```{r firstchoice-and-religion, fig.height=6, fig.width=7, echo = FALSE, include = FALSE}
newfirst %>% 
  ggplot(newfirst, mapping = aes(x = (factor(howreligious ,levels=c("Not at all religious", "Not very religious", "Somewhat religious", "Religious", "Very religious"))), fill = firstchoice))+
  geom_bar(position= "fill") +
  labs(title = "was duke your first choice vs. religiousity", 
       x = "", y = "") +
  coord_flip() +
  theme_minimal()
```

```{r fig.height=6, fig.width=7, echo = FALSE}
newfirst %>% 
  ggplot(newfirst, mapping = aes(fill = (factor(compactOp,levels=c("Strongly unfavorable", "Somewhat unfavorable", "No opinion", "Somewhat favorable", "Strongly favorable"))), x = (factor(president ,levels=c("Joe Biden","Donald Trump")))))+
  geom_bar(position= "fill") +
  labs(title = "view of Duke Compact and presidential vote", 
  subtitle = "NOTE: Howie Hawkins and Jo Jorgenson removed from data set.
            One student voted for each candidate.",
       x = "", y = "") +
  scale_fill_discrete(name = "view of Duke Compact") +
  scale_x_discrete(na.translate = FALSE) +
  coord_flip() +
  theme_minimal()
```

```{r fig.height=6, fig.width=7}
newfirst %>% 
  ggplot(data=subset(newfirst, !is.na(political)), mapping = aes(x = (factor(compactOp,levels=c("Strongly favorable", "Somewhat favorable", "No opinion", "Somewhat unfavorable", "Strongly unfavorable"))), fill = (factor(political ,levels=c("Very conservative", "Somewhat conservative", "Moderate","Somewhat liberal", "Very liberal")))))+
  geom_bar(position= "fill") +
  labs(title = "view of Duke Compact and political leaning", 
       x = "", y = "") +
  scale_fill_discrete(name = "political leaning") +
  scale_x_discrete(na.translate = FALSE) +
  coord_flip() +
  theme_minimal()
```

Students who voted for Joe Biden have more favorable views of the Duke 
Compact. Similarly, students who identify themselves as somewhat or very liberal 
(on a scale of Very conservative to Very liberal) have more favorable views of 
the Duke Compact.

```{r fig.height=6, fig.width=7, echo = FALSE}
newfirst %>% 
  ggplot(newfirst, mapping = aes(fill = (factor(enforcementOp,levels=c("Strongly unfavorable", "Somewhat unfavorable", "No opinion", "Somewhat favorable", "Strongly favorable"))), x = (factor(president ,levels=c("Joe Biden","Donald Trump")))))+
  geom_bar(position= "fill") +
  labs(title = "view of Duke Compact enforcement and presidential vote", 
  subtitle = "NOTE: Howie Hawkins and Jo Jorgenson removed from data set.
            One student voted for each candidate.",
       x = "", y = "") +
  scale_fill_discrete(name = "view of Duke Compact enforcement") +
  scale_x_discrete(na.translate = FALSE) +
  coord_flip() +
  theme_minimal()
```

```{r fig.height=6, fig.width=7}
newfirst %>% 
  ggplot(data=subset(newfirst, !is.na(political)), mapping = aes(x = (factor(enforcementOp,levels=c("Strongly favorable", "Somewhat favorable", "No opinion", "Somewhat unfavorable", "Strongly unfavorable"))), fill = (factor(political ,levels=c("Very conservative", "Somewhat conservative", "Moderate","Somewhat liberal", "Very liberal")))))+
  geom_bar(position= "fill") +
  labs(title = "view of Duke Compact enforcement and political leaning", 
       x = "", y = "") +
  scale_fill_discrete(name = "political leaning") +
  scale_x_discrete(na.translate = FALSE) +
  coord_flip() +
  theme_minimal()
```

Students who voted for Trump have a more unfavorable view of Duke Compact 
enforcement. When view of Duke Compact is analyzed with an eye to political
leaning, no trend is immediately evident. 

## How are liberals/conservatives adhering to the Duke Compact? (I hate this too)

```{r fig.height=6, fig.width=7}
newfirst %>% 
  ggplot(data=subset(newfirst, !is.na(political)), mapping = aes(fill = (factor(political ,levels=c("Very conservative", "Somewhat conservative", "Moderate","Somewhat liberal", "Very liberal"))), x = (factor(report, levels =c("Very likely", "Moderately likely", "Neither likely nor unlikely","Moderately unlikely", "Very unlikely")))))+
  geom_bar(position= "fill") +
  labs(title = "likelihood of reporting compact violations & political leaning", 
       x = "", y = "") +
  scale_fill_discrete(name = "political leaning") +
  coord_flip() +
  theme_minimal()
```

There is no pattern with regards to political leaning and likelihood of 
reporting Duke Compact violations. However...

```{r fig.height=6, fig.width=7}
newfirst %>% 
  ggplot(data=subset(newfirst, !is.na(political)), mapping = aes(fill = (factor(political ,levels=c("Very conservative", "Somewhat conservative", "Moderate","Somewhat liberal", "Very liberal"))), x = (factor(wearmask, levels=c("Very likely", "Moderately Likely", "Neither likely or unlikely")))))+
  geom_bar(position= "fill") +
  labs(title = "likelihood of wearing a mask vs. political leaning", 
       x = "", y = "") +
  scale_fill_discrete(name = "political leaning") +
  coord_flip() +
  scale_x_discrete(na.translate = FALSE) +
  theme_minimal()
```

Somewhat conservative students and Very conservative students are more likely to
indicate that they are Moderately likely or Neither likely or unlikely to wear a
mask...

```{r fig.height=6, fig.width=7, include=FALSE}
newfirst %>% 
  ggplot(newfirst, mapping = aes(fill = (factor(political ,levels=c("Very conservative", "Somewhat conservative", "Moderate","Somewhat liberal", "Very liberal"))), x = (factor(usesymmon, levels=c("Very likely", "Moderately Likely", "Neither likely or unlikely", "Moderately unlikely")))))+
  geom_bar(position= "fill") +
  labs(title = "likelihood of using symmon vs. political leaning", 
       x = "", y = "") +
  scale_fill_discrete(name = "political leaning") +
  coord_flip() +
  scale_x_discrete(na.translate = FALSE) +
  theme_minimal()
```

```{r fig.height=6, fig.width=7}
newfirst %>% 
  ggplot(newfirst, mapping = aes(fill = (factor(political ,levels=c("Very conservative", "Somewhat conservative", "Moderate","Somewhat liberal", "Very liberal"))), x = (factor(avoidgather, levels =c("Very likely", "Moderately Likely", "Neither likely nor unlikely","Moderately unlikely", "Very unlikely")))))+
  geom_bar(position= "fill") +
  labs(title = "likelihood of avoiding gatherings vs. political leaning", 
       x = "", y = "") +
  scale_fill_discrete(name = "political leaning") +
  coord_flip() +
  scale_x_discrete(na.translate = FALSE) +
  theme_minimal()
```

and Somewhat conservative and Moderate students are more likely to indicate that
they are Very unlikely to avoid gatherings.